The pollination trade-off

### 2018-11-13 paper/manuscript.Rmd
Count also words in abstract

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
drake::loadd(msc_wordcount)
```

**Manuscript length:** approx. `r format(msc_wordcount$n_words_stri, big.mark = ",")` words including abstract and awknoledgements, `r msc_wordcount$reading_time_stri` reading time.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, 
                      warning = FALSE)
```

```{r draft-details}
drake::loadd(msc_wordcount, abs_wordcount)
```

**Manuscript length:** `r format(msc_wordcount$n_char_tot_stri, big.mark = ",")` characters; approx. `r format(round(msc_wordcount$n_words_stri/10)*10-90, big.mark = ",")` words (includes draft info, excludes front-matter, abstract, awknoledgements, references, and figure/table legends); `r msc_wordcount$reading_time_stri` reading time.

**Abstract length:** `r abs_wordcount$n_words_stri` words.
